Stochastic Wind Power Forecasting

### 2020-05-31 LaTeX_Code/Paper/paper_1line.tex
start intro

>>>>

Despite the Covid-19 pandemic caused ``the biggest shock to the global energy system in more than seven decades'' and the recent report released on April 30, 2020, by the International Energy Agency (\url{https://www.iea.org/reports/global-energy-review-2020}) stresses that projections of energy demand will fall 6\% in 2020 - seven times the decline after the 2008 global financial crisis - it is emphasized that ``renewables are set to be the only energy source that will grow in 2020, with their share of global electricity generation projected to jump thanks to their priority access to grids and low operating cost'' (\cite{IEA}).

Although the growth of renewables in electricity generation in 2020 is set to be lower than in previous years,  solar PV and wind are on track to help lift renewable electricity generation by 5\% in 2020, aided by higher output from hydropower. \\

Wind and solar energy are expanding renewable generation capacity, experiencing record growth in the last years.
